SciPy - some descriptive title here

### 2018-04-12 scipy-1.0/paper.tex
MAINT: Pinned the location of Table 1 to prevent interjection into asv subsection.
MAINT: add paragraph on `asv continuous`

% Packages
\usepackage[super]{nth}
\usepackage{rotating}
\usepackage{makecell}
\usepackage{pifont}
\usepackage{amsfonts}
\usepackage{amsmath}

@@

\subsection*{Submodule organisation}

@@

    Consider the following asv benchmark results, spanning roughly nine years of project history, that demonstrate the gradual performance
    improvements in \texttt{scipy.spatial.cKDTree.query()} (nearest-neighbor search) performance, using command:

@@

    \begin{figure}[!ht]
        \centering
        \includegraphics[width=\textwidth]{static/asv_time_query_ckdtree}
        \caption{Airspeed velocity benchmarks for scipy.spatial.cKDTree.query() over a roughly nine year commit history time frame. The results are based on Python 2.7 performance on the master branch of the project using numpy 1.8.2 and Cython versions 0.27.3 and 0.21.1 (for improved backward compatibility). Only the L2 (Euclidean) norm is shown here, and to improve backward compatibility / sampling of the benchmarks there was no application of toroidal topology to the KDTree (boxsize argument was ignored).}
    \end{figure}

>>>>

% Packages
\usepackage[super]{nth}
\usepackage{rotating}
\usepackage{makecell}
\usepackage{pifont}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{float}

@@

\subsection*{Submodule organisation}
\input{subpackages}

@@

    Consider the following asv benchmark results, spanning roughly nine years of project history. These demonstrate the gradual performance
    improvements in a nearest-neighbor search, \texttt{scipy.spatial.cKDTree.query()} using the command:

@@

   Any pull request can be compared against the \texttt{master} branch with the command \texttt{asv continuous master new-feature}. This will provide a benchmark against the master branch and the branch a new feature is implemented in. More features are available in the documentation, including arguments to select which benchmarks to run.

    \begin{figure}[H]
        \centering
        \includegraphics[width=\textwidth]{static/asv_time_query_ckdtree}
        \caption{Airspeed velocity benchmarks for scipy.spatial.cKDTree.query() over a roughly nine year commit history time frame. The results are based on Python 2.7 performance on the master branch of the project using numpy 1.8.2 and Cython versions 0.27.3 and 0.21.1 (for improved backward compatibility). Only the L2 (Euclidean) norm is shown here, and to improve backward compatibility and sampling of the benchmarks there was no application of toroidal topology to the KDTree (boxsize argument was ignored).}
    \end{figure}
